---
title: "SDS Final Project"
authors: Laura Fay, Abby Kaufman, Casey MacGibbon
format:
  html:
    self-contained: true
---
```{r, echo = FALSE}
library(ggplot2)
library(tidyverse)
library(dplyr)
legos <- read.csv("https://wjhopper.github.io/SDS-201/data/legos.csv")
```

## Introduction
Background information paragraph on legos + prices maybe affordibility for kids

To address this question, we used a dataset from 

Filtered, outcome variable and also our explanatory vars

```{r}
ggplot(data = legos, aes(x= Pieces)) + geom_histogram()
```

The data has a clear right skew, with most of the lego sets having between 0 and 1,000 pieces. 

```{r, echo = FALSE}
ggplot(data = legos,aes( x = Pieces, y = Price, color = Minifigures)) + geom_point() + scale_color_continuous(low = "pink", high = "maroon")
```

##Trying to find the mean price of the legos by brand, but we're confused why some brands have NA values
```{r}
mean_price_legos <- legos %>% filter(!is.na(legos)) %>% group_by(Theme) %>% summarize(mean_price = mean(Price))
```

##Plot of mean prices, but many large themes have NA
```{r}
ggplot(data = legos, aes(y= Theme, x= mean_price)) + geom_col()
```

